---
title: "IFN701: Zillow's Home Value Prediction (Zestimate) --- 2016"
author: "Linni, QIN n9632981"
output:
  pdf_document: default
  html_document: default
---


# Call the useful packages

```{r}
library(ggplot2)

library(plyr)

#install.packages("dplyr")
library(dplyr)

#install.packages("corrplot")
library(corrplot)

#library(ggmap)

#install.packages("Metrics")
library(Metrics)


#install.packages("caret")# to identify the importance of the feature
library(caret)
#install.packages("mlbench")
library(mlbench)
#install.packages("randomForest")
library(randomForest)

```


# Import the available data

```{r,fig.width=10, fig.height=7}

train16_cm <- read.csv("./train_2016_v2.csv", header = TRUE) # keep the name of the month for plotting
train16_nm <- read.csv("./train_2016_v2.csv", header = TRUE) # convert to number month for prediction laster
prop16 <- read.csv("./properties_2016.csv", header = TRUE)
colnames(prop16)
```


## 1. Data Analysis


```{r}
# convert the date into the name of the month for further visulation analysis
train16_cm$month <- months(as.Date(train16_cm$transactiondate, format = "%d/%m/%y"))
train16_nm$month <- months(as.Date(train16_cm$transactiondate, format = "%d/%m/%y"))


train16_nm$transactiondate <- gsub("[/]", "" , train16_nm$transactiondate, perl=TRUE)
train16_nm$transactiondate <- as.numeric(train16_nm$transactiondate)
train16_nm$month <- match(train16_nm$month, month.name)
is.numeric(train16_nm$month)
```


```{r}

summarise(train16_cm, Median=median(train16_cm$logerror), Mean= mean(train16_cm$logerror), Max=max(train16_cm$logerror), Min=min(train16_cm$logerror), Std=sd(train16_cm$logerror)) 

```

# Variable Importance

http://topepo.github.io/caret/variable-importance.html

```{r,fig.width=10, fig.height=10}

mergeid <- merge(x=train16_nm, y=prop16, by = "parcelid", all.x = TRUE)

mergeidA <- select_if(mergeid,is.numeric) # correlationship is calculated with numeric value only

mergeidA <- replace(mergeidA, is.na(mergeidA), 0)

A <- cor(mergeidA) 
#corrplot(A, method="circle") # first exploration

mergeidAn <- mergeidA[,!(colnames(mergeidA) == "assessmentyear")]
mergeidAtest <- select(mergeidAn, parcelid, logerror, month, bathroomcnt, bedroomcnt, fips, latitude, longitude,  propertylandusetypeid, roomcnt, taxvaluedollarcnt, calculatedfinishedsquarefeet, yearbuilt)
#B <- cor(mergeidAn) 
#corrplot(B, method="circle") # first exploration

#highlyCorrelated <- findCorrelation(B, cutoff = 0.5)
#print(highlyCorrelated)

```



```{r}
set.seed(7)
data(mergeidAtest)
inTraining <- createDataPartition(mergeidAtest$logerror, p=0.7, list=FALSE)
training <- mergeidAtest[inTraining,]
testing <- mergeidAtest[-inTraining,]
modelFit <- train(logerror~., data = training, method="rf", importance=TRUE)
gbmImp <- varImp(modelFit, scale=FALSE)
# cannot run..cause R die.

```









methods <- c('boot', 'boot632', 'cv', 'repeatedcv', 'LOOCV', 'LGOCV')

```{r}

set.seed(7)
ind <- sample(2,nrow(mergeidAn), replace=TRUE, prob = c(0.7, 0.3))

train1 <- mergeidAn[ind==1,]
test1 <- mergeidAn[ind==2,]
control <- trainControl(method = "LOOCV", number = 100)# repeats = 10 for repeatedcv method only
model <- train(logerror~., data = mergeidAn, method = "lvq", preProcess="scale", trControl=control)
importance <- varImp(model, scale=FALSE)
print(importance)
plot(importance)

```
```{r}

set.seed(7)
data(mergeidAn)
control2 <- rfeControl(functions=rfFuncs, method = "cv", number = 100)# repeats = 10 for repeatedcv method only
results2 <- rfe(mergeidAn[,3:55],mergeidAn[,55], sizes=c(3:55), rfeControl=control2)
print(results2)
predictors(results2)


```

#### try to use decision tree model to prediction the logeeror with 11 above explored useful features 
#### divide the logerror into different 31 classes with interval 0.01 (range -0.15 --- +0.15  )


```{r}
p11 <- subset(mergeid, logerror < "-0.15" & logerror < "0") 
#confirm the subset results
p11[which.max(p11$logerror),]
p11[which.min(p11$logerror),]

p12 <- subset(mergeid, logerror == "0") 
p13 <- subset(mergeid, logerror > "0" &logerror < "0.15") 
p13[which.max(p13$logerror),]
p13[which.min(p13$logerror),]

p1 <- rbind(p11,p12,p13)
p1[which.max(p1$logerror),]
p1[which.min(p1$logerror),]

p1 <- select(p1, parcelid, logerror, month, bathroomcnt, bedroomcnt, fips, latitude, longitude,  propertylandusetypeid, roomcnt, taxvaluedollarcnt, calculatedfinishedsquarefeet, yearbuilt)

p1$taxvaluedollarcnt <- replace(p1$taxvaluedollarcnt, is.na(p1$taxvaluedollarcnt), 0)

p1$calculatedfinishedsquarefeet <- replace(p1$calculatedfinishedsquarefeet, is.na(p1$calculatedfinishedsquarefeet), 0)

p1$yearbuilt <- replace(p1$yearbuilt, is.na(p1$yearbuilt), 0)

p2 <- data.frame(colSums(!is.na(p1)))
names(p2)[1] <- c("values")

print(p2)


```



### Multiple Linear Regression

https://www.tutorialspoint.com/r/r_multiple_regression.htm
http://www.r-tutor.com/elementary-statistics/multiple-linear-regression/estimated-multiple-regression-equation
http://r-statistics.co/Linear-Regression.html (ACCURACY)


## TEST1 7:3 (10 variables)
```{r}

set.seed(100)
test1 <- sample(1:nrow(p1), 0.7*nrow(p1))
train1<- p1[test1,]
test1 <- p1[-test1,]

```

```{r}

model1_a = lm(logerror ~ bathroomcnt + bedroomcnt + fips + latitude + longitude + propertylandusetypeid + roomcnt + taxvaluedollarcnt + calculatedfinishedsquarefeet + yearbuilt, data = train1)

summary(model1_a)

```




```{r}

pre1_a <- data.frame(predict(model1_a, test1)) 
summary(pre1_a)
plot(pre1_a)
summary(test1$logerror)
```
```{r}

mse(pre1_a,test1$logerror)
```


# Calculate prediction accuracy rates 


## TEST 2 7:3 (8 variables, delete latitude & longitude)

```{r}

model1_b = lm(logerror ~ bathroomcnt + bedroomcnt + fips + propertylandusetypeid + roomcnt + taxvaluedollarcnt + calculatedfinishedsquarefeet + yearbuilt, data = train1)
pre1_b <- data.frame(predict(model1_b, test1)) 
pre1_bnold <- data.frame(cbind(origin=test1$logerror, pred=pre1_b))
cor_accuracy1_b <- cor(pre1_bnold)
print(cor_accuracy1_b) #10.4%
mse(pre1_b,test1$logerror)

```

## TEST 3 7:3 (5 variables, delete bathroomcnt & bedroomcnt & roomcnt)
```{r}

model1_c = lm(logerror ~  fips + propertylandusetypeid + taxvaluedollarcnt + calculatedfinishedsquarefeet + yearbuilt, data = train1)
pre1_c <- data.frame(predict(model1_c, test1)) 
pre1_cnold <- data.frame(cbind(origin=test1$logerror, pred=pre1_c))
cor_accuracy1_c <- cor(pre1_cnold)
print(cor_accuracy1_c) #9.8%
mse(pre1_c,test1$logerror)

```

```{r}

model1_d = lm(logerror ~  fips , data = train1)
pre1_d <- data.frame(predict(model1_d, test1)) 
pre1_dnold <- data.frame(cbind(origin=test1$logerror, pred=pre1_d))
cor_accuracy1_d <- cor(pre1_dnold)
print(cor_accuracy1_d) 
mse(pre1_d,test1$logerror)
lm.beta(model1_d) # it is said online that cor value doesnot work for some regression variable but the stand cor


```



# After talking to Guido

NO need to care about the varibales, just focus on the train16 data. Use the month and detail date as vaiable to find out if prediction score varying with the size of the data.

```{r}

jan <- subset(train16_nm, month == "1")
feb <- subset(train16_nm, month == "2")
mar <- subset(train16_nm, month == "3")
apr <- subset(train16_nm, month == "4")
may <- subset(train16_nm, month == "5")
jun <- subset(train16_nm, month == "6")
jul <- subset(train16_nm, month == "7")
aug <- subset(train16_nm, month == "8")
sep <- subset(train16_nm, month == "9")
oct <- subset(train16_nm, month == "10")
nov <- subset(train16_nm, month=="11")
dec <- subset(train16_nm, month =="12")

```



Month by Month: Train = the 1st day of the month till the last but the 7 days left


```{r}
(ddply(jan, .(transactiondate), "nrow"))
train_jan <- subset(jan, transactiondate < "25012016")
test_jan<- subset(jan, transactiondate >= "25012016")

```

```{r}

model_jan = lm(logerror ~  transactiondate, data = train_jan)
pre_jan <- data.frame(predict(model_jan, test_jan)) 

mse(pre_jan,test_jan$logerror)

```



```{r}
(ddply(feb, .(transactiondate), "nrow"))
train_feb <- subset(feb, transactiondate < "23022016")
test_feb<- subset(jan, transactiondate >= "23022016")

```

```{r}

model_feb = lm(logerror ~  transactiondate, data = train_feb)
pre_feb <- data.frame(predict(model_feb, test_feb)) 

mse(pre_feb,test_feb$logerror)

```


```{r}

jf <- rbind(jan,feb)
train_jf <- subset(jf, transactiondate < "23022016")
test_jf<- subset(jf, transactiondate >= "23022016")

model_jf = lm(logerror ~  transactiondate, data = train_jf)
pre_jf <- data.frame(predict(model_jf, test_jf)) 

mse(pre_jf,test_jf$logerror) # predcit the whole feb 0.03293103


```



```{r}

train_mar <- subset(mar, transactiondate < "25032016")
test_mar<- subset(mar, transactiondate >= "25032016")
model_mar = lm(logerror ~  transactiondate, data = train_mar)
pre_mar <- data.frame(predict(model_mar, test_mar)) 

mse(pre_mar,test_mar$logerror)

```

```{r}
jfm<-rbind(jan,feb,mar)
train_jfm <- subset(jfm, transactiondate < "25032016")
test_jfm<- subset(jfm, transactiondate >= "25032016")
model_jfm = lm(logerror ~  transactiondate, data = train_jfm)
pre_jfm <- data.frame(predict(model_jfm, test_jfm)) 

mse(pre_jfm,test_jfm$logerror) # predict the whole mar:0.02927437

```

```{r}

train_apr <- subset(apr, transactiondate < "24042016")
test_apr<- subset(apr, transactiondate >= "24042016")
model_apr = lm(logerror ~  transactiondate, data = train_apr)
pre_apr <- data.frame(predict(model_apr, test_apr)) 

mse(pre_apr,test_apr$logerror)

```

```{r}
jfma<-rbind(jan,feb,mar,apr)
train_jfma <- subset(jfma, transactiondate < "24042016")
test_jfma<- subset(jfma, transactiondate >= "24042016")
model_jfma = lm(logerror ~  transactiondate, data = train_jfma)
pre_jfma <- data.frame(predict(model_jfma, test_jfma)) 

mse(pre_jfma,test_jfma$logerror) # value for predict the whole apr 0.03204248

```

```{r}

train_may <- subset(may, transactiondate < "25052016")
test_may<- subset(may, transactiondate >= "25052016")
model_may = lm(logerror ~  transactiondate, data = train_may)
pre_may <- data.frame(predict(model_may, test_may)) 

mse(pre_may,test_may$logerror)

```
```{r}
jfmam<-rbind(jan,feb,mar,apr,may)
train_jfmam <- subset(jfmam, transactiondate < "25052016")
test_jfmam<- subset(jfmam, transactiondate >= "25052016")
model_jfmam = lm(logerror ~  transactiondate, data = train_jfmam)
pre_jfmam <- data.frame(predict(model_jfmam, test_jfmam)) 

mse(pre_jfmam,test_jfmam$logerror) # similar value if it predict the whole may 0.02939354

```

```{r}

train_jun <- subset(jun, transactiondate < "24062016")
test_jun<- subset(jun, transactiondate >= "24062016")
model_jun = lm(logerror ~  transactiondate, data = train_jun)
pre_jun <- data.frame(predict(model_jun, test_jun)) 

mse(pre_jun,test_jun$logerror)

```


```{r}
jfmamj<-rbind(jan,feb,mar,apr,may,jun)
train_jfmamj <- subset(jfmamj, transactiondate < "24062016")
test_jfmamj<- subset(jfmamj, transactiondate >= "24062016")
model_jfmamj = lm(logerror ~  transactiondate, data = train_jfmamj)
pre_jfmamj <- data.frame(predict(model_jfmamj, test_jfmamj)) 

mse(pre_jfmamj,test_jfmamj$logerror) # the same vaule if it predict the whole jun 0.2823762

```



```{r}

train_jul <- subset(jul, transactiondate < "25072016")
test_jul<- subset(jul, transactiondate >= "25072016")
model_jul = lm(logerror ~  transactiondate, data = train_jul)
pre_jul <- data.frame(predict(model_jul, test_jul)) 

mse(pre_jul,test_jul$logerror)

```
```{r}
jfmamjj<-rbind(jan,feb,mar,apr,may,jun,jul)
train_jfmamjj <- subset(jfmamjj, transactiondate < "25072016")
test_jfmamjj<- subset(jfmamjj, transactiondate >= "25072016")
model_jfmamjj = lm(logerror ~  transactiondate, data = train_jfmamjj)
pre_jfmamjj <- data.frame(predict(model_jfmamjj, test_jfmamjj)) 

mse(pre_jfmamjj,test_jfmamjj$logerror) # 0.02758651 if it predict the whole july

```


```{r}

train_aug <- subset(aug, transactiondate < "25082016")
test_aug<- subset(aug, transactiondate >= "25082016")
model_aug = lm(logerror ~  transactiondate, data = train_aug)
pre_aug <- data.frame(predict(model_aug, test_aug)) 

mse(pre_aug,test_aug$logerror)

```

```{r}
jfmamjja<-rbind(jan,feb,mar,apr,may,jun,jul,aug)
train_jfmamjja <- subset(jfmamjja, transactiondate < "25082016")
test_jfmamjja<- subset(jfmamjja, transactiondate >= "25082016")
model_jfmamjja = lm(logerror ~  transactiondate, data = train_jfmamjja)
pre_jfmamjja <- data.frame(predict(model_jfmamjja, test_jfmamjja)) 

mse(pre_jfmamjja,test_jfmamjja$logerror) # 0.02664009 if it predict the whole aug

```

```{r}

train_sep <- subset(sep, transactiondate < "24092016")
test_sep<- subset(sep, transactiondate >= "24092016")
model_sep = lm(logerror ~  transactiondate, data = train_sep)
pre_sep <- data.frame(predict(model_sep, test_sep)) 

mse(pre_sep,test_sep$logerror)

```


```{r}
jfmamjjas<-rbind(jan,feb,mar,apr,may,jun,jul,aug,sep)
train_jfmamjjas <- subset(jfmamjjas, transactiondate < "24092016")
test_jfmamjjas<- subset(jfmamjjas, transactiondate >= "24092016")
model_jfmamjjas = lm(logerror ~  transactiondate, data = train_jfmamjjas)
pre_jfmamjjas <- data.frame(predict(model_jfmamjjas, test_jfmamjjas)) 

mse(pre_jfmamjjas,test_jfmamjjas$logerror) # 0.02715848 if it predict the whole sep

```

```{r}

train_oct <- subset(oct, transactiondate < "25102016")
test_oct<- subset(oct, transactiondate >= "25102016")
model_oct = lm(logerror ~  transactiondate, data = train_oct)
pre_oct <- data.frame(predict(model_oct, test_oct)) 

mse(pre_oct,test_oct$logerror)

```

```{r}
jfmamjjaso<-rbind(jan,feb,mar,apr,may,jun,jul,aug,sep,oct)
train_jfmamjjaso <- subset(jfmamjjaso, transactiondate < "25102016")
test_jfmamjjaso<- subset(jfmamjjaso, transactiondate >= "25102016")
model_jfmamjjaso = lm(logerror ~  transactiondate, data = train_jfmamjjaso)
pre_jfmamjjaso <- data.frame(predict(model_jfmamjjaso, test_jfmamjjaso)) 

mse(pre_jfmamjjaso,test_jfmamjjaso$logerror) # 0.02600165 if it predict the whole sep

```


```{r}

train_nov <- subset(nov, transactiondate < "24112016")
test_nov<- subset(nov, transactiondate >= "24112016")
model_nov = lm(logerror ~  transactiondate, data = train_nov)
pre_nov <- data.frame(predict(model_nov, test_nov)) 

mse(pre_nov,test_nov$logerror)
#(ddply(nov, .(transactiondate), "nrow")) # mse is lower than others, smaller size of transaction

```

```{r}
jfmamjjason<-rbind(jan,feb,mar,apr,may,jun,jul,aug,sep,oct,nov)
train_jfmamjjason <- subset(jfmamjjason, transactiondate < "24112016")
test_jfmamjjason<- subset(jfmamjjason, transactiondate >= "24112016")
model_jfmamjjason = lm(logerror ~  transactiondate, data = train_jfmamjjason)
pre_jfmamjjason <- data.frame(predict(model_jfmamjjason, test_jfmamjjason)) 

mse(pre_jfmamjjason,test_jfmamjjason$logerror) # 0.02573006 if it predict the whole nov

```


```{r}

train_dec <- subset(dec, transactiondate < "24122016")
test_dec<- subset(dec, transactiondate >= "24122016")
model_dec = lm(logerror ~  transactiondate, data = train_dec)
pre_dec <- data.frame(predict(model_dec, test_dec)) 

mse(pre_dec,test_dec$logerror) # larger than others, but still smaller size of transaction


```

```{r}
jfmamjjasond<-rbind(jan,feb,mar,apr,may,jun,jul,aug,sep,oct,nov,dec)
train_jfmamjjasond <- subset(jfmamjjasond, transactiondate < "24122016")
test_jfmamjjasond<- subset(jfmamjjasond, transactiondate >= "24122016")
model_jfmamjjasond = lm(logerror ~  transactiondate, data = train_jfmamjjasond)
pre_jfmamjjasond <- data.frame(predict(model_jfmamjjasond, test_jfmamjjasond)) 

mse(pre_jfmamjjasond,test_jfmamjjasond$logerror) # 0.02619549 if it predict the whole dec

```


























